Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-07 sections/01-introduction.tex
Update on Overleaf.

The evaluation of trending is also interesting for the assessment of nowcasts.
, nowcasting focuses on predicting the current status.

Nowcasting methods are now widely used in other fields, such as economics and medicine, and focus on predictions for the present, the immediate future, and the recent past (\cite{banbura2013now, bok2018macroeconomic, wolffram2023collaborative}).
Nowcasting has its origins in meteorology, and the methods were originally developed to describe the current state of the weather in detail and to predict the expected change on a time scale of a few hours (\cite{browning1989nowcasting,schmid2019nowcasting}).

Nowcasting can be used, for example, to predict important statistics such as the current economic situation (e.g. GDP), which are collected with low frequency and are available with a considerable time delay (\cite{banbura2013now}).
Nowcasting methods use indicators that are related to the target variable but can be collected at a higher frequency and published in a timely manner to produce and update early estimates for the target variable (e.g. GDP from the first quarter of 2024 ) during the relevant period (i.e. from January to March 2024) (\cite{castle2017forecasting}). 
In medicine, epidemic nowcasting is used during an ongoing epidemic to assess the current situation, taking into account the main pathogenic, epidemiological, clinical, and socio-behavioral factors (\cite{wu2021nowcasting}). 
The nowcasting method can be used, for example, to correct the daily Covid case numbers for events that have occurred but have not yet been reported before this data has been fully recorded at a central location (\cite{gunther2021nowcasting}). 
In this context, nowcasting is an estimation procedure in which the value of a target variable (e.g. from today) is estimated on the basis of current preliminary measurements, which is only finalised at a later point in time. 
At the time of the forecast, estimates of the target variable can be made for today and possibly for yesterday (if the value for yesterday has not yet been finalised); the predicted change in the target variable is then the difference between the two nowcast values. 
A nowcast is consistent with the development of the target variable if the difference in the actual value between today and yesterday, which is announced at a later date, has the same sign as the predicted change. 
A nowcast with strong trending ability provides crucial information on the development of the target variable (e.g. the number of cases of an epidemic) and can be a solid basis for decisions on the introduction or cancellation of policy measures. like forecasts, nowcasts are often evaluated and compared in the literature on the basis of performance measures such as the root mean absolute error (\cite{gunther2021nowcasting}) and the aspect of trending ability is not considered in the literature to the best of our knowledge.

>>>>

The evaluation of trending is also interesting for the assessment of nowcasts.
In contrast to conventional forecasting methods, Nowcasting methods focus on predictions for the present, the immediate future, and the recent past (\cite{banbura2013now}) and are now widely used in fields, such as economics and medicine (\cite{bok2018macroeconomic, wolffram2023collaborative}).
Nowcasting has its origins in meteorology, and the methods were originally developed to describe the current state of the weather in detail and to predict the expected change on a time scale of a few hours (\cite{browning1989nowcasting,schmid2019nowcasting}). In economics, Nowcasting can be used, for example, to predict important statistics such as the current economic situation (for example, GDP), which are collected with low frequency and are available with a considerable time delay (\cite{banbura2013now}).
Nowcasting methods use indicators that are related to the target variable but can be collected at a higher frequency and published in a timely manner to produce and update early estimates for the target variable during the relevant period (\cite{castle2017forecasting}). For example, in the context of forecasting GDP, we use economic indicators collected at a higher frequency from January to March 2024 to forecast GDP from the first quarter of 2024, before the official statistics are published.
In medicine, epidemic nowcasting is used during an ongoing epidemic to assess the current situation, taking into account the main pathogenic, epidemiological, clinical, and socio-behavioral factors (\cite{wu2021nowcasting}). 
The nowcasting method can be used, for example, to correct the daily Covid case numbers for events that have occurred but have not yet been reported before this data has been fully recorded at a central location (\cite{gunther2021nowcasting}). 
In this context, nowcasting is an estimation procedure in which the value of a target variable (e.g. from today) is estimated on the basis of current preliminary measurements, which is only finalised at a later point in time.

A nowcast with strong trending ability provides crucial information on the development of the target variable (e.g. the number of cases of an epidemic) and can be a solid basis for decisions on the introduction or cancellation of policy measures. like forecasts, nowcasts are often evaluated and compared in the literature on the basis of performance measures such as the root mean absolute error (\cite{gunther2021nowcasting}) and the aspect of trending ability is not considered in the literature to the best of our knowledge.
